Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-13 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
Update oregon_cvd_pulm_results.Rmd

```{r health data import, message=F, warning=F}
# importing case-crossover dataframes 
# SABA case-crossover will be imported first
# i can't find a lot of the files
# asthma
asthma_path <- paste0("./data/health/2017-oregon_casecross_asthma.csv")
asthma_df <- read_csv(asthma_path)

# cvd 
cvd_path <- paste0("./data/health/2017-oregon_casecross_cvd.csv")
cvd_df <- read_csv(cvd_path)
# had a warning message for cvd dataframe import; should check on this

@@

# I think purrr would be a good way to loop through a list of outcome dataframes
# bind dataframes in a list
outcome_df_list <- list(asthma_df, cvd_df)

# name list elements in order I'd like to present in document
# commented out for now.
# outcome_names <- c("SABA", "Respiratory", "Asthma", "COPD", "Pneumonia", 
#   "Acute Bronchitis", "Cardiovascular Disease", "Arrhythmia", 
#   "Cerebrovascular Disease", "Heart Failure", "Ischemic Heart Disease", 
#   "Myocardial Infarction")
outcome_names <- c("Asthma", "CVD")

names(outcome_df_list) <- c( 'Asthma', 'CVD')
```

>>>>

```{r health data import, message=F, warning=F}
# importing case-crossover dataframes 
# SABA case-crossover will be imported first

# SABA
saba_path <- paste0("./data/health/2013-oregon_casecross_saba.csv")
saba_df <- read_csv(saba_path)

# respiratory
respiratory_path <- paste0("./data/health/2013-oregon_casecross_respiratory.csv")
respiratory_df <- read_csv(respiratory_path)

# asthma
asthma_path <- paste0("./data/health/2013-oregon_casecross_asthma.csv")
asthma_df <- read_csv(asthma_path)

# COPD
copd_path <- paste0("./data/health/2013-oregon_casecross_copd.csv")
copd_df <- read_csv(copd_path)

# pneumonia
pneumonia_path <- paste0("./data/health/2013-oregon_casecross_pneumonia.csv")
pneumonia_df <- read_csv(pneumonia_path)

# acute bronchitis
acute_bronch_path <- paste0("./data/health/2013-oregon_casecross_acute_bronch.csv")
acute_bronch_df <- read_csv(arrhythmia_path)

# Cardiovascular Disease
cvd_path <- paste0("./data/health/2013-oregon_casecross_cvd.csv")
cvd_df <- read_csv(cvd_path)
# had a warning message for cvd dataframe import; should check on this

# arrhythmia
arrhythmia_path <- paste0("./data/health/2013-oregon_casecross_arrhythmia.csv")
arrhythmia_df <- read_csv(arrhythmia_path)

# Cerebrovascular Disease
cerbrovas_dis_path <- paste0("./data/health/2013-oregon_casecross_cerbrovas_dis.csv")
cerbrovas_dis_df <- read_csv(cerbrovas_dis_path)

# Heart Failure
heart_failure_path <- paste0("./data/health/2013-oregon_casecross_heart_failure.csv")
heart_failure_df <- read_csv(heart_failure_path)

# Ischemic Heart Disease
isch_heart_dis_path <- paste0("./data/health/2013-oregon_casecross_isch_heart_dis.csv")
isch_heart_dis_df <- read_csv(isch_heart_dis_path)

# Myocardial Infarction
myocardial_infarc_path <- paste0("./data/health/2013-oregon_casecross_myocardial_infarc.csv")
myocardial_infarc_df <- read_csv(myocardial_infarc_path)

@@

# I think purrr would be a good way to loop through a list of outcome dataframes
# bind dataframes in a list
outcome_df_list <- list(saba_df, respiratory_df, asthma_df, copd_df, pneumonia_df, 
                        acute_bronch_df, cvd_df, arrhythmia_df, cerbrovas_dis_df, 
                        heart_failure_df, isch_heart_dis_df, myocardial_infarc_df)

# name list elements in order I'd like to present in document
# commented out for now.
outcome_names <- c("SABA", "Respiratory", "Asthma", "COPD", "Pneumonia", 
                   "Acute Bronchitis", "Cardiovascular Disease", "Arrhythmia", 
                   "Cerebrovascular Disease", "Heart Failure", "Ischemic Heart Disease", 
                   "Myocardial Infarction")

names(outcome_df_list) <- c('SABA', 'Respiratory', 'Asthma', 'COPD', 'Pneumonia', 
                            'Acute Bronchitis', 'Cardiovascular Disease', 'Arrhythmia', 
                            'Cerebrovascular Disease', 'Heart Failure', 
                            'Ischemic Heart Disease', 'Myocardial Infarction')

# try athma
outcome_df_list <- list(asthma_df)

outcome_names <- c("Asthma")

names(outcome_df_list) <- c('Asthma')

```
